Supplementary Materials

### 2020-09-04 analysis/analysis.Rmd
minor edits

```{r}
d_eeg %>% group_by(subject) %>% 
  summarise(count = n()) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

@@

```{r}
d_dispthresh %>% group_by(subject) %>% summarise(count = n()) %>% knitr::kable()
```

@@

### Subgroup Relationships
Import subgroup information and display a table of the relationships that we will be investigating.

@@

Now we will use it!

@@

## Replicatation of Kohler et al (2016)

We can look at the groups that only contain orientation, and see if we obtain the parametric response as documented in Kohler et al. (2016). We will also investigate if we see the corresponding pattern with the display duration threshold data, with the time taken to detect the symmetry dreasing as we increase the amount of rotational symmetry.

```{r, cache = TRUE}
d_eeg %>% filter(wg %in% c("P2", "P3", "P4", "P6")) %>%
  mutate(orientation = parse_number(wg))-> d_eeg_rot

m_eeg_rot <- brm(data = d_eeg_rot, rms ~ orientation + (1|subject), family = "lognormal")

@@

d_eeg_rot %>% modelr::data_grid(orientation) %>%
  add_fitted_draws(m_eeg_rot, re_formula = NA, n=200) %>%
  ggplot() + 
  geom_line(data = d_eeg_rot, aes(x = orientation, y = rms, group = subject), alpha = 0.1, colour = "darkred") +
  geom_path(aes(x = orientation, y = .value, group = .draw), alpha = .1, colour = "royalblue2") + 
  theme_minimal() -> p1
```
```{r, cache = TRUE}
d_dispthresh %>% filter(wg %in% c("P2", "P3", "P4", "P6")) %>%
  mutate(orientation = parse_number(wg))-> d_disp_rot

m_disp_rot <- brm(data = d_disp_rot, threshold ~ orientation + (1|subject), family = "lognormal")

@@

d_disp_rot %>% modelr::data_grid(orientation) %>%
  add_fitted_draws(m_disp_rot, re_formula = NA, n=200) %>%
  ggplot() + 
  geom_line(data = d_disp_rot, aes(x = orientation, y = threshold, group = subject), alpha = 0.1, colour = "red") +
  geom_path(aes(x = orientation, y = .value, group = .draw), alpha = .1, colour = "royalblue2") + 
  theme_minimal() -> p2
```

@@

@@

summary(my_models$disp)

@@

print(bR2)

@@

d %>%
  modelr::data_grid(rms = seq(-0.2, 1, 0.1)) %>%
  add_fitted_draws(m, n = 100) %>%
  ggplot(aes(x = rms, y = threshold, color = as.factor(index))) +
  geom_line(aes(y = .value, group = .draw), alpha = .1, colour = "thistle4") +
  geom_point(data = d) +
  theme_minimal() +
  ggthemes::scale_colour_ptol("index")

>>>>

@@

```{r}
d_dispthresh %>% 
  group_by(subject) %>% 
  summarise(count = n()) %>% 
  knitr::kable() %>% 
  kableExtra::kable_styling(full_width = F)
```

@@

### Subgroup Relationships
Import subgroup information and display a table of the relationships that we will be investigating. Relationships taken from Coxeter & Moser (1972).

@@

@@

## Replication of Kohler et al (2016)

We can look at the groups that only contain rotations, and see if we obtain the parametric response as documented in Kohler et al. (2016).

```{r, cache = TRUE}
d_eeg %>% filter(wg %in% c("P2", "P3", "P4", "P6")) %>%
  mutate(rotation = parse_number(wg))-> d_eeg_rot

m_eeg_rot <- brm(data = d_eeg_rot, rms ~ rotation + (1|subject), family = "lognormal")

@@

d_eeg_rot %>% modelr::data_grid(rotation) %>%
  add_fitted_draws(m_eeg_rot, re_formula = NA, n=200) %>%
  ggplot() + 
  geom_line(data = d_eeg_rot, aes(x = rotation, y = rms, group = subject), alpha = 0.1, colour = "darkred") +
  geom_path(aes(x = rotation, y = .value, group = .draw), alpha = .1, colour = "royalblue2") + 
  theme_minimal() -> p1
```

We will also investigate if we see the corresponding pattern with the display duration threshold data, with the time taken to detect the symmetry dreasing as we increase the amount of rotational symmetry.

```{r, cache = TRUE}
d_dispthresh %>% filter(wg %in% c("P2", "P3", "P4", "P6")) %>%
  mutate(rotation = parse_number(wg))-> d_disp_rot

m_disp_rot <- brm(data = d_disp_rot, threshold ~ rotation + (1|subject), family = "lognormal")

@@

d_disp_rot %>% modelr::data_grid(rotation) %>%
  add_fitted_draws(m_disp_rot, re_formula = NA, n=200) %>%
  ggplot() + 
  geom_line(data = d_disp_rot, aes(x = rotation, y = threshold, group = subject), alpha = 0.1, colour = "red") +
  geom_path(aes(x = rotation, y = .value, group = .draw), alpha = .1, colour = "royalblue2") + 
  theme_minimal() -> p2
```

@@

summary(my_models$eeg)
```

@@

summary(my_models$disp)
```

It is unclear from the above summary tables whether either variable has a clear effect. We can use leave-one-out metrics to compare models.

```{r}
summary(lm(data = comp_summary$threshold, mean_value ~ index * normal))
summary(lm(data = comp_summary$eeg, mean_value ~ index * normal))

@@

print(bR2)
```

@@

d %>%
  modelr::data_grid(rms = seq(-0.2, 1, 0.1)) %>%
  add_fitted_draws(m, n = 100) %>%
  ggplot(aes(x = rms, y = threshold, color = as.factor(index))) +
  geom_line(aes(y = .value, group = .draw), alpha = .1, colour = "thistle4") +
  geom_point(data = d) +
  theme_minimal() +
  ggthemes::scale_colour_ptol("index")
```
